My Cool Title

### 2019-05-04 paper.tex
Starting description of android implementation
Added section on results, figures on time to target

\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{amsmath}

@@

\begin{table}
  \centering
  \caption{The reward function for the POMDP. }\label{tab:rewards}
  \begin{tabular}{cc}
    \toprule
    $r(o = o_{target})$ & 10000 \\ \midrule
    $r(v = \texrm{true})$  & -75 \\ \midrule
    $r(n > n_{\max})$ & -75 \\ \midrule
    otherwise $r(\cdot)$ & -100  \\ \midrule
    \bottomrule
  \end{tabular}
\end{table}

@@

@@

>>>>

\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{amsmath}
\usepackage{subcaption}
\usepackage{caption}

@@

\begin{table}
  \centering
  \caption{The reward function for the POMDP. }\label{tab:rewards}
  \begin{tabular}{cc}
    \toprule
    $r(o = o_{target})$ & 10000 \\ \midrule
    $r(v = \textrm{true})$  & -75 \\ \midrule
    $r(n > n_{\max})$ & -75 \\ \midrule
    otherwise $r(\cdot)$ & -100  \\ \midrule
    \bottomrule
  \end{tabular}
\end{table}

@@

We made an Android app that implements the object detector and POMDP controller onto a mobile phone that can generate and provide guidance instructions for a user.

@@

%\subsection{Target Acquisition}

\subsection{Time to Target}

The time it took a participant to find a target object is an important indicator of performance for the system, where less time indicates a shorter search time and increased performance.
The data for the search times for each dataset are given in Fig~\ref{fig:boxplot-time}, while Fig.~\ref{fig:cum-time} shows the cumulative distribution functions (CDF) for the search times as a function of the total number of objects found.

\begin{figure}
  \begin{subfigure}{0.5\textwidth}
    \centering
    \includegraphics[width=0.9\textwidth]{figures/boxplot_time_to_target.png}
    \caption{A set of boxplots comparing the time to target. }\label{fig:boxplot-time}
  \end{subfigure}
  \begin{subfigure}{0.5\textwidth}
    \centering
    \includegraphics[width=0.9\textwidth]{figures/cumplot_time_to_target.png}
    \caption{A set of CDFs comparing the time to target. }\label{fig:cum-time}
  \end{subfigure}
  \caption{A set of boxplots and CDFs comparing the time it took the participants to find the targets for each experiments. }
\end{figure}

By inspecting the boxplots in Fig.~\ref{fig:boxplot-time}, it can be seen that the guidance system reduced the time it took the participants to find the targets on average from 17.8s to 10s per target, ($p = 0.038$).
This is an average improvement of almost 40\%.
This is supported by the CDFs in Fig.~\ref{fig:cum-time} that show that \todo{Discuss the less number of objects found and how it is not statistically signioficatn. Perhaps show it in CDF}

\subsection{Movement}

To give an indication of the effort required to find each target, we look at the mobile device's displacement data. 
In this case, less device displacement is desirable, since it implies less physical exertion was demanded from the user, enhancing the user experience\todo{maybe cite paper that says less exertion is good}.

The device displacement was both linear and angular in the $x, y, z, \phi$ (pan) and $\theta$ dimensions.
By integrating these data with respect to time, we can get the total displacement for each dimension.
